---
title: "Flex Dashboards for Sharing Results"
output:
  flexdashboard::flex_dashboard:
    source_code: embed
    orientation: columns
    theme: cosmo
editor_options: 
  chunk_output_type: console
---

```{r, libraries, include = FALSE}
## here to navigate project directory
library(here)

## tidyverse for data wrangling and visualization
library(tidyverse)

## snakecase for naming conventions
library(snakecase)

## flexdashboard to build dashboards in R Markdown
library(flexdashboard)

## shiny for reactive dashboards
library(shiny)

## jsonlite to import json data files
library(jsonlite)

## hexbin for hex plots
library(hexbin)

## DT for web-friendly, interactive tables
library(DT)
```

```{r, global, include = FALSE}
### import data objects
## use read_json() to import the data file
airline <- read_json(
  ## use here() to locate file in our project directory
  here(
    # folder
    "data", 
    # file
    "airline.json"
  ),
  ## turn into data table
  simplifyVector = TRUE
)

### rename variables, convert variables
## overwrite 
airline <- airline %>%
  ## convert to tibble
  as_tibble() %>%
  ## mutate variable types and values
  mutate(
    ## characters to factors
    across(
      # find character variables
      .cols = where(is.character),
      # convert to factors
      .fns = as_factor
    ),
    ## relevel
    Class = fct_relevel(
      # factor
      Class, 
      # level
      "Business", 
      # position
      after = 2
    )
  ) %>%
  ## clean variable names
  rename_with(
    # function
    .fn = to_snake_case
  )
```

```{css, echo = FALSE}
/* adjust height of data tables */
.dataTables_scrollBody {
  /* adjust height */
  max-height: 100% !important;
}
```

```{r, gauge_compute, include = FALSE}
### display table
## call data
gauge_compute <- airline %>%
  ## groups
  group_by(
    # travel 
    travel_type
  ) %>%
  ## compute summaries
  summarize(
    # count
    count = n(),
    # mean recommendation
    mean_recommend = format(
      # round
      round(
        # average
        mean(recommendation),
        # decimals
        digits = 2
      ),
      # decimals
      nsmall = 2
    ),
    # remove groups
    .groups = "drop"
  )
```

Plots 
================

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Violin Plot

```{r, plot_1}
### violin plot
## call data and mapping
ggplot(
  # data
  airline,
  # mapping
  aes(
    # x-axis
    x = customer_type, 
    # y-axis
    y = recommendation, 
    # fill
    fill = class
  )
) +
  ## violin geometry
  geom_violin() +
  ## labels
  labs(
    # x-axis
    x = "Customer Type", 
    # y-axis
    y = "Recommendation", 
    # fill
    fill = "Class"
  )
```

### Hex Bin Plot 

```{r, plot_2}
### hex plot
## call data and mapping
ggplot(
  # data
  airline,
  # mapping
  aes(
    # x-axis
    x = age, 
    # y-axis
    y = recommendation
  )
) +
  ## hex geometry
  geom_hex() +
  ## labels
  labs(
    # x-axis
    x = "Age", 
    # y-axis
    y = "Recommendation", 
    # fill
    fill = "Count"
  )
```

### Heat Map

```{r, plot_3}
### heat map
## call data and mapping
ggplot(
  # data
  airline,
  # mapping
  aes(
    # x-axis
    x = leg_room, 
    # y-axis
    y = cleanliness, 
    # fill
    fill = recommendation
  )
) +
  ## tile geometry
  geom_tile() +
  ## adjust fill color
  scale_fill_gradient2(
    # low value color
    low = "blue",
    # mid value color
    mid = "white",
    # high value color
    high = "red",
    # midpoint
    midpoint = 50
  ) +
  ## labels
  labs(
    # x-axis
    x = "Leg Room", 
    # y-axis
    y = "Cleanliness", 
    # fill
    fill = "Recommendation"
  )
```

### 2D Density Plot

```{r, plot_4}
### filled 2d density
## call data and mapping
ggplot(
  # data
  airline,
  # mapping
  aes(
    # x-axis
    x = flight_distance, 
    # y-axis
    y = recommendation
  )
) +
  ## tile geometry
  geom_density_2d_filled(
    # contours
    contour_var = "ndensity"
  ) +
  ## facet
  facet_grid(
    # rows by columns
    customer_type ~ class
  ) +
  ## labels
  labs(
    # x-axis
    x = "Flight Distance", 
    # y-axis
    y = "Recommendation", 
    # fill
    fill = "Density"
  )
```

Table 1 {data-navmenu=Tables} 
================

Column
-----------------------------------------------------------------------

### Younger Female Customers

```{r, table_1}
### filtered table
## save
tab_1 <- airline %>%
  ## filter for rows
  filter(
    # condition
    age <= 30,
    # condition
    gender == "Female"
  ) %>%
  ## select columns
  select(
    # filter variables
    age, gender,
    # other characteristics
    customer_type, travel_type:flight_distance,
    # measures
    inflight_wi_fi:recommendation
  )

### display table
## datatable
datatable(
  # data
  tab_1,
  # remove row names
  rownames = FALSE, 
  # filter
  filter = "top",
  # add buttons
  extensions = "Scroller",
  # options
  options = list(
    # table, length, pagination, scrolling
    dom = "tlpS",
    # scroller
    scrollY = "200px",
    # number of rows
    pageLength = 25
  )
)
```

Table 2 {data-navmenu=Tables} 
================

Column
-----------------------------------------------------------------------

### Older Female Customers

```{r, table_2}
### filtered table
## save
tab_2 <- airline %>%
  ## filter for rows
  filter(
    # condition
    age > 30,
    # condition
    gender == "Female"
  ) %>%
  ## select columns
  select(
    # filter variables
    age, gender,
    # other characteristics
    customer_type, travel_type:flight_distance,
    # measures
    inflight_wi_fi:recommendation
  )

### display table
## datatable
datatable(
  # data
  tab_2,
  # remove row names
  rownames = FALSE, 
  # filter
  filter = "top",
  # add buttons
  extensions = "Scroller",
  # options
  options = list(
    # table, length, pagination, scrolling
    dom = "tlpS",
    # scroller
    scrollY = "200px",
    # number of rows
    pageLength = 25
  )
)
```

Gauges
================

Column
-----------------------------------------------------------------------

### Personal Travel Customers

```{r, box_1}
### value box
## call function
valueBox(
  ## data
  gauge_compute %>%
    ## filter
    filter(
      # condition
      travel_type == "Personal Travel"
    ) %>%
    ## extract value
    pull(count),
  # caption
  caption = "Number of Personal Travel Customers",
  # icon
  icon = "fa-chart-bar"
)
```

### Average Recommendation of Personal Travel Customers

```{r, gauge_1}
### gauge
## call function
gauge(
  ## data
  gauge_compute %>%
    ## filter
    filter(
      # condition
      travel_type == "Personal Travel"
    ) %>%
    ## extract value
    pull(mean_recommend),
  ## minimum and maximum
  min = 0, max = 100,
  ## sectors
  sectors = gaugeSectors(
    # green
    success = c(75, 100),
    # orange
    warning = c(50, 74),
    # red
    danger = c(0, 49)
  )
)
```

Column
-----------------------------------------------------------------------

### Business Travel Customers

```{r, box_2}
### value box
## call function
valueBox(
  ## data
  gauge_compute %>%
    ## filter
    filter(
      # condition
      travel_type == "Business Travel"
    ) %>%
    ## extract value
    pull(count),
  # caption
  caption = "Number of Business Travel Customers",
  # icon
  icon = "fa-chart-bar"
)
```

### Average Recommendation of Business Travel Customers

```{r, gauge_2}
### gauge
## call function
gauge(
  ## data
  gauge_compute %>%
    ## filter
    filter(
      # condition
      travel_type == "Business Travel"
    ) %>%
    ## extract value
    pull(mean_recommend),
  ## minimum and maximum
  min = 0, max = 100,
  ## sectors
  sectors = gaugeSectors(
    # green
    success = c(75, 100),
    # orange
    warning = c(50, 74),
    # red
    danger = c(0, 49)
  )
)
```

Storyboard {.storyboard}
================

### Younger Female Customers Clustered by Satisfaction and Recommendation

```{r, clusters_1}

cluster_1 <- airline %>%
  filter(age <= 30, gender == "Female") %>%
  select(recommendation, satisfaction)

set.seed(123)  # Set seed for reproducibility
kmeans_cluster_1 <- kmeans(cluster_1, centers = 3, nstart = 25)

cluster_1 <- cluster_1 %>%
  mutate(cluster = factor(kmeans_cluster_1$cluster))

ggplot() +
  # First geom_point layer with cluster_1 data
  geom_point(data = cluster_1, aes(x = satisfaction, y = recommendation, color = cluster), size = 2) +
  # Second geom_point layer with cluster centers
  geom_point(data = as_tibble(kmeans_cluster_1$centers), aes(x = satisfaction, y = recommendation, color = factor(1:3)), 
             size = 4, shape = 4, stroke = 4) +
  # Label the axes and legend
  labs(x = "Satisfaction", y = "Recommendation", color = "Cluster") +
  # Update the theme
  theme(legend.position = "bottom")

```

***

We create three clusters of **younger female customers** as a function of their flight satisfaction and recommendation.
We see the clusters defined by either low, medium, or high values on both variables.
Next step requires investigating what we do well to make these customers satisfied and willing to recommend our airline.

### Older Female Customers Clustered by Satisfaction and Recommendation

```{r, cluster_2}
cluster_2 <- airline %>%
  filter(age > 30, gender == "Female") %>%
  select(recommendation, satisfaction)

set.seed(123)  # Set seed for reproducibility
kmeans_cluster_2 <- kmeans(cluster_2, centers = 3, nstart = 25)

cluster_2 <- cluster_2 %>%
  mutate(cluster = factor(kmeans_cluster_2$cluster))

ggplot() +
  # First geom_point layer with cluster_2 data
  geom_point(data = cluster_2, aes(x = satisfaction, y = recommendation, color = cluster), size = 2) +
  # Second geom_point layer with cluster centers
  geom_point(data = as_tibble(kmeans_cluster_2$centers), aes(x = satisfaction, y = recommendation, color = factor(1:3)), 
             size = 4, shape = 4, stroke = 4) +
  # Label the axes and legend
  labs(x = "Satisfaction", y = "Recommendation", color = "Cluster") +
  # Update the theme
  theme(legend.position = "bottom")
```

***

We create three clusters of **older female customers** as a function of their flight satisfaction and recommendation.
We see the clusters defined by either low, medium, or high values on both variables.
Next step requires investigating what we do well to make these customers satisfied and willing to recommend our airline.
